\chapter*{Definitions and Abbreviations}\label{chap:additional_chapters}

\addcontentsline{toc}{chapter}{Definitions and Abbreviations}

Here is a list of abbreviations used throughout the research, along with their short definitions:

\begin{enumerate}
    \item \textbf{IoT} - Internet of Things: A network of interconnected devices and sensors that communicate and share data over the internet.
    \item \textbf{MCU} - Microcontroller Unit: A small, integrated computer on a single chip, used for embedded systems and control applications.
    \item \textbf{UWB} - Ultra-Wideband: A radio technology that uses a wide frequency range for high data rate, short-range communication.
    \item \textbf{MCM} - Monte Carlo Method: A computational method that uses random sampling to solve complex problems and estimate results.
    \item \textbf{GA} - Genetic Algorithm: A search heuristic inspired by natural selection and genetics, used to optimize complex problems.
    \item \textbf{mA} - milliampere: A unit of electric current equal to one-thousandth of an ampere.
    \item \textbf{uA} - microampere: A unit of electric current equal to one-millionth of an ampere.
    \item \textbf{dBm} - decibel-milliwatts: A unit of power level used to express the ratio of power in decibels relative to 1 milliwatt.
    \item \textbf{WSN} - Wireless Sensor Network: A network of small, low-power devices that communicate wirelessly.
    \item \textbf{RF} - Radio Frequency: Electromagnetic wave frequencies used for wireless communication.
    \item \textbf{dB} - decibel: A unit of measurement used to express the ratio of two values in a logarithmic scale.
    \item \textbf{FTD} - Full Thread Device: A node in a Thread network capable of routing traffic and participating in network management functions.
    \item \textbf{MTD} - Minimal Thread Device: A node in a Thread network with limited routing capabilities, primarily functioning as an end device for low-power operation.
    \item \textbf{STD} - Sleepy Thread Device: A low-power node in a Thread network that periodically wakes up to communicate before returning to sleep mode.
    \item \textbf{SoC} - System on a Chip: An integrated circuit that combines multiple electronic components, such as a microprocessor, memory, and interfaces, on a single chip.
    \item \textbf{nRF} - Nordic Semiconductor's RF series: A family of wireless SoCs developed by Nordic Semiconductor, designed for ultra-low power consumption and high-performance wireless connectivity.
\end{enumerate}
